A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-25 paper.tex
Harold's edits to intro

The small (1 mm) nematode \emph{Caenorhabditis elegans} (\emph{C. elegans}) has become widely used as a model organism \citep{corsi2015}, and has been among the most widely studied biological models of neuronal development, locomotion and the central pattern generator \citep{katz2016}.
The C. elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).  There are a variety of neuronal models which can generate such undulation,
``When crawling on a solid surface, the nematode C. elegans moves forward by propagating sinusoidal dorso-ventral retrograde contraction waves.  A uniform propagating wave leads to motion that undulates about a straight line.'' \citep{kim2011}.
A different type of locomotion, often called swimming, occurs when nematodes are submerged in a liquid medium. The nematodes “switch” between these two gaits, under the regulation of particular serotonergic and dopaminergic neurons.

@@

In addition to simulating the CPG, we also implemented a modified version of the FitzHugh-Nagumo neuron, originally proposed by \citet{keener1983}, as an analog circuit.  This circuit solves the Keener differential equations, and we adjusted it to allow diffusive coupling between neurons.  We made a small network with these ``neuro-mimetic'' circuits, and showed that their behaviour replicates FitzHugh-Nagumo simulated behaviour.

There are many other models for the CPG; for example, a 2019 preprint by \cite{olivares2019} proposes a distributed network of oscillating systems, instead of a structured chain like our proposed CPG.  The point of this paper is to create a minimal working model, though, and not to strive for full realism.

>>>>

The small (1 mm) nematode \emph{Caenorhabditis elegans} (\emph{C. elegans}) has become widely used as a model organism (cf. http://www.wormbook.org \cite{corsi2015}), and has been among the most widely studied biological models of neuronal development and locomotion \citep{katz2016, corsi2015}.
The C. elegans connectome has been completely mapped \citep{jabr} and, as described below, its locomotion has been widely studied (\citet{corsi2015}).  There are a variety of neuronal models which can generate such undulation,
``When crawling on a solid surface, the nematode C. elegans moves forward by propagating sinusoidal dorso-ventral retrograde contraction waves.  A uniform propagating wave leads to motion that undulates about a straight line.'' \citep{kim2011}.
A different type of locomotion, often called swimming, occurs when nematodes are submerged in a liquid medium. The nematodes “switch” between these two gaits, under the regulation of particular serotonergic and dopaminergic neurons.

@@

Finally, we describe an analog electronic implementation of our model through solving a modified version of the FitzHugh-Nagumo neuron \cite{fitzhugh1955}, based upon an analog circuit originally proposed by \citet{keener1983}.  This circuit solves the Keener differential equations, and we adjusted it to allow diffusive coupling between neurons.  We made a small network with these ``neuro-mimetic'' circuits, and showed that their behaviour replicates FitzHugh-Nagumo simulated behaviour.

There are many other models for the CPG; for example, a 2019 preprint by \cite{olivares2019} proposes a distributed network of self-oscillating systems of neurons, instead of a structured chain like our proposed CPG.  The point of this paper is to create a minimal working model, though, and not to strive for full realism.
